---
output:
  pdf_document: default
  html_document: default
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.pos = 'h')
```

# 1) Who am I?

Hello. My name is Helen Casendino. I am at the start of my third year of undergraduate education in the School of Aquatic and Fisheries Sciences. I grew up in Orinda, California, and came up to Seattle excited about experiencing a *four-season year*. Now that I have been here a few years, I may return to the sun — but we'll see. Outside of my academics, I enjoy art (painting) and dance. I'm lucky enough that I have been able to enroll in an in-person dance class this quarter. I'm looking forward to the end of the pandemic so that all the arts can be experienced in person again. 

# 2) What do I study?

The two research projects I am a part of at the moment relate to marine invertebrate diseases. Individually, I am looking into sea star wasting disease in subtidal zones of the Puget Sound. I also assist a postdoc in the Wood Lab studying polydora spp. infection in Pacific oysters.  

### Keywords

* marine invertebrate diseases 
* climate change impacts 
* trophic cascade

# 3) What do I want from this course?

1. How to use Rmarkdown 
2. How to do model selection 
3. How to create mixed effects models 

# 4) Plot air quality data

```{r airquality, fig.height = 4, fig.width = 5, fig.align = "center", fig.cap="Air Quality vs. Ozone", echo = FALSE}
boxplot(airquality$Ozone~airquality$Month, xlab="Month", ylab="Ozone")
```


\vspace{0.25in}

# 5) Say it with an equation


$$
y_{1,2} = \alpha + \beta_{1} x_{1} + \beta_{2} x_{2} + e_{1,2} \\
$$
$y_{1,2}$ is the dependent variable.  
$\beta_{1}$ is the coefficient for $x_{1}$, which is the first dependent variable. 
$\beta_{2}$ is the coefficient for $x_{2}$, which is the second dependent variable. 
$\alpha$ and $e_{1,2}$ are additional parameters.  


